Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-06 ipsj/paper.tex
Add TECS development flow

>>>>

\subsubsection{開発フロー}

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/TECSFlow.pdf}
    \caption{Development flow using TECS}
    \label{fig:TECSFlow}
\end{figure}

Fig. \ref{fig:TECSFlow} shows the development flow using TECS.
TECS generator generates the interface code (.H and .C) and the configure file of the RTOS (.cfg) from the CDL file.

Software developers using TECS can be divided into component designers and application developers.
Component designers define signatures, which are interfaces between cells, and celltypes, which are types of cells.
Using the template code generated from the CDL file in which these are defined, component designers implement the functions and behaviors of the component in C language.
The source code implementing the function of the component is called a celltype code.
Application developers develop applications by using component diagrams and predefined celltype to connect cells with build description.
An application module is generated by compiling and linking the header, the interface code, and the celltype code.
